%-------------------------
% Resume in Latex
% Author : Nilanjan Nayak
% Website: https://github.com/nylenx/resume
%------------------------


\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}
\usepackage{fontawesome5}
\usepackage[dvipsnames]{xcolor}
\usepackage{tikz}
\usepackage{multicol}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{{\Large Nilanjan Nayak}} & Email : \href{mailto:ifnilanjan@gmail.com}{ifnilanjan@gmail.com}\\
    
  \href{https://www.linkedin.com/in/nilanjan-nayak-75b289202/} {
    \begin{tikzpicture}
        \node[scale=1,RoyalBlue] at (0,0){\faIcon{linkedin}/in/nilanjan-nayak-75b289202};
    \end{tikzpicture}} & 
    Mobile : +91-700-181-7312 \\

\end{tabular*}


%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {OneMed \& A2Z Solutions Pvt Ltd.}{Kolkata, WB}
      {Digital Marketing Executive}{Feb 2024 - Present}
      \resumeItemListStart
        \resumeItem{SEO}
          {Responsible for optimizing website content and structure to improve search engine rankings, drive organic traffic, and enhance overall online visibility.}
        \resumeItem{Analytics}
          {Utilize SEO tools such as SEMrush, Google Analytics, and Search Console to monitor and analyze website performance, identify areas for improvement, and track progress effectively.}
        \resumeItem{Automation}
          {Develop and implement \href{https://www.selenium.dev/}{\textbf{SELENIUM}} automation scripts to efficiently collect and manage potential lead data from various online platforms.}
      \resumeItemListEnd

    \resumeSubheading
      {Intelmetic LTD}{Kolkata, WB}
      {Associate Software Engineer}{Aug 2021 - Aug 2023}
      \resumeItemListStart
        \resumeItem{Notifications}
          {Service for sending email, push and in-app notifications. Involved in features such as delivery time optimization, tracking, queuing and A/B testing. Built an internal app to run batch campaigns for marketing etc.}
        \resumeItem{Nostos}
          {Bulk data processing and injection service from Hadoop to Cassandra and provides a thin REST layer on top for serving offline computed data online.}
        \resumeItem{Workflows}
          {Dataduct an open source workflow framework to create and manage data pipelines leveraging reusables patterns to expedite developer productivity.}
        \resumeItem{Data Collection}
          {Designed the internal survey and crowd sourcing platfowm which allowed for creating various tasks for crowd sourding or embedding surveys across the Coursera platform.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd
  

%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Camellia Institute of Technology}{North 24 pgs, WB}
      {Bachelor of Science in Computer Science;  CGPA: 8.15}{Aug. 2021 -- July. 2024}
    \resumeSubheading
      {Central Calcutta Polytechnic (Govt. of W.B)}{Kolkata, WB}
      {Diploma in Computer Science \& Technology;  PERCENTAGE: 86\%}{Jul. 2019 -- Aug. 2021}
  \resumeSubHeadingListEnd


\section{{tools \& Technologies}}
\begin{multicols}{2}
\begin{itemize}
    \item Programming Languages: Python, JavaScript, Java
    \item Web Technologies: HTML, CSS, JavaScript
    \item Frameworks: ReactJS, NextJS
    \item Cloud Technology: AWS services
    \item Database Management: MySQL, MongoDB
    \item Version Control: Git, Bitbucket
    \item Other Tools: Adobe XD, Figma
\end{itemize}
\end{multicols}


%-----------PROJECTS-----------------
\section{Projects}
  \resumeSubHeadingListStart
  
      \resumeSubheading
        {CulinaryMate}{  
          \href{https://www.gihub.com/} {
          \begin{tikzpicture}
              \node[scale=1,Fuchsia] at (0,0){\faIcon{github}};
          \end{tikzpicture}}
          }
        {Your culinary guide with ingredient detection and tailored recipe suggestions.}
        
      \resumeSubheading
      {Certi-fly}{  
         \href{https://www.gihub.com/} {
          \begin{tikzpicture}
              \node[scale=1,Fuchsia] at (0,0){\faIcon{github}};
          \end{tikzpicture}}
          }
          {Workshop certification issuance for bulk participants without storage, while maintaining a streamlined  process.} 
  
  \resumeSubHeadingListEnd


%-----------Certification-----------------
\section{Certification}
  \resumeSubHeadingListStart
    \resumeSubheading
      {SQL}{
        \href{https://www.hackerrank.com/}{HackerRank}
        }
      {Skilled in SQL for database management, complex queries, and performance optimization.}

    \resumeSubheading
      {Python}{
        \href{https://www.hackerrank.com/}{HackerRank}
      }
      {Proficient in Python for automation, data analysis, web development, and scripting.}
  \resumeSubHeadingListEnd
  

%-------------------------------------------
\end{document}